Application of Network Flow and Linear Programming to Scheduling of Clinicians

### 2019-08-19 paper/paper.results.tex
Remove 2017 table + use adjustbox to scale table

\subsection{Infectious Diseases Division}
We use clinician time-off requests and minimum/maximum requirements from 2015-2018 as input data for the LP problem. Tables \ref{tbl:2017-schedule-comparison}, \ref{tbl:2018-schedule-comparison}, \ref{??}, \ref{??} present the optimal schedule generated using the software as well as the manually created schedule, color-coded to distinguish between the different clinicians assigned.

\include{tbl/2017_schedule_comparison}
\include{tbl/2018_schedule_comparison}

>>>>

\subsection{Infectious Diseases Division}
We use clinician time-off requests and minimum/maximum requirements from 2015-2018 as input data for the LP problem. Table \ref{tbl:2018-schedule-comparison} presents a the optimal schedule generated using the software as well as the manually created schedule for data from 2018, color-coded to distinguish between the different clinicians assigned.

\include{tbl/2018_schedule_comparison}
